SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-11 docs/questioning.tex
some typos

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistenly present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
source code to applications by using a variety of
languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, duirng the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
% even if
% some of them share characteristics with supported frameworks
% like Mozilla's Content Security
% Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
% ({\sc csp}) and Google
% Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06},
the majority of them are not used in practice.

>>>>

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
source code to applications by using a variety of
languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
% even if
% some of them share characteristics with supported frameworks
% like Mozilla's Content Security
% Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
% ({\sc csp}) and Google
% Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06},
the majority of them are not used in practice.
